
% Ch.04-01   | Introduction
\section{Apache Spark}

\begin{frame}
    \frametitle{Course Objectives}

    \begin{itemize}
        \item Understand the fundamentals of Apache Spark.
        \item Build data processing applications using Apache Spark.
        \item Understand Apache Spark APIs (RDD, DataFrames, and Datasets).
        \item Optimize and tune Apache Spark applications.
        \item Build streaming applications using Apache Spark.
        \item Build scalable machine learning applications using Apache Spark MLlib.
        \item Deploy Apache Spark in production environments.
    \end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Course References}
\begin{frame}
    \frametitle{\subsecname}
    \begin{itemize}
        \item \href{https://pages.databricks.com/rs/094-YMS-629/images/LearningSpark2.0.pdf}{Learning Spark, 2nd Edition} By Jules S. Damji, Brooke Wenig, Tathagata Das, Denny Lee.
        \item \href{https://learning.oreilly.com/library/view/spark-the-definitive/9781491912201/}{Spark: The Definitive Guide} By Bill Chambers, Matei Zaharia.
        \item Random blog posts.
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Course Prerequisites}
\begin{frame}
    \frametitle{\subsecname}
    Before beginning this course, participants should have:
    \begin{itemize}
        \item Experience in programming using Python.
        \item Basic programming skills using shell.
        \item An understanding of MapReduce foundations and Hive. \href{https://www.youtube.com/playlist?list=PLxNoJq6k39G8Ak39PDC-oYvp6ZRvIn3Pa}{Garage Education YouTube Playlist}
    \end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
